### 2015-05-13 whoop.tex
trimming down limitations

\medskip\noindent\textbf{Limitations }
%
\whoop is based on lockset analysis and thus can report false bugs, because a violation of the locking discipline does not always correspond to a real data race (e.g.\ when lockfree synchronization is used instead of locking). \whoop also uses over-approximation (e.g.\ when reading from the shared state) and summarization, which can be sources of false positives. Furthermore, the tool does not currently check for dynamically created locks or for locks that are provided by external libraries, although the later could be addressed by providing a mechanism for users to declare custom locks. We also do not currently handle interrupt handlers in a special way; to be sound, we assume that they can execute concurrently with entry points at any time. We could address this in the future by modeling interrupt-specific kernel functions (e.g. for enabling/disabling interrupts).

>>>>

\medskip\noindent\textbf{Limitations }
%
As a lockset analyzer, \whoop can be imprecise because a violation of the locking discipline does not always correspond to a real race (e.g.\ when lockfree synchronization is used). \whoop also over-approximates drivers, which can be another source of imprecision. Furthermore, the tool does not check for dynamically created locks or for locks provided by external libraries, although the later could be addressed by providing a mechanism for users to declare custom locks. We also do not currently treat interrupt handlers in a special way; we just assume that they can execute concurrently with any entry point. One way to address this is to model interrupt-specific kernel functions (e.g. for enabling/disabling interrupts).
